---
output: github_document
---

## imputeTestbench

#### *Neeraj Bokde, neerajdhanraj@gmail.com, Marcus W. Beck, mbafs2012@gmail.com*

[![R-CMD-check](https://github.com/fawda123/imputeTestbench/workflows/R-CMD-check/badge.svg)](https://github.com/fawda123/imputeTestbench/actions)
[![Downloads from the RStudio CRAN mirror](http://cranlogs.r-pkg.org/badges/grand-total/imputeTestbench)](https://CRAN.R-project.org/package=imputeTestbench)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the development repository for the imputeTestbench package.  This package provides a testbench for comparing imputation methods for missing data in univariate time series. 

The development version of this package can be installed from GitHub:

```{r, eval = FALSE}
install.packages('devtools')
library(devtools)
install_github('neerajdhanraj/imputeTestbench', ref = 'development')
```

The current release can be installed from CRAN:

```{r, eval = FALSE}
install.packages('imputeTestbench')
```

Load the package after installation:

```{r, eval = FALSE}
library(imputeTestbench)
```
```{r, echo = F, message = F, warning = F}
devtools::load_all()
```

#### Basic use

The core function is `impute_errors()`.  See the help documentation for more details.

```{r message = F, warning = F}
a <- impute_errors(data = nottem)
a
plot_errors(a, plotType = 'line')
```

#### Citation

Beck MW, Bokde N, Ascencio-Cortes G, Kulat K (2018). "R package imputeTestbench to Compare Imputation Methods for
Univarite Time Series." _The R Journal_, *10*(1), 218-233. doi: 10.32614/RJ-2018-024 (URL:
http://doi.org/10.32614/RJ-2018-024).

#### Bug reports 

Please submit any bug reports (or suggestions) using the [issues](https://github.com/neerajdhanraj/imputeTestbench/issues) tab of the GitHub page.

#### License

This package is released in the public domain under the creative commons license CC0.
